\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{margin=1in}

\title{Homework 4:\\A New Golden Age for Computer Architecture}
\author{Pupipat Singkhorn}
\date{\today}

\begin{document}

\maketitle

\section*{Introduction}

We live in a world that is constantly changing. As you graduate from this course, you should keep up with current trends and emerging techniques. This assignment serves as a practice for your lifelong learning journey. You will read a review article that talks about the past, the present, and the future of computer architecture. Even though the past might seem boring and irrelevant at first, you will notice that many of the techniques in the past keep reappearing in new forms. This is true in many fields of study.

You will find many concepts that we learned in the course, and it should serve as a good review.

This exercise will have you read and answer questions based on a recent article by computer architecture experts, John L. Hennessy and David A. Patterson.

You can access the article by going to the materials section in MCV.

\section*{Questions}

\begin{enumerate}
    \item According to the CPU time formula, why is RISC better than CISC?

    : answer here

    \item Why did the `Itanic' ISA become unused?

    \item What type of parallel architecture according to Flynn's taxonomy is Itanic?

    \item Explain `Dennard scaling' in your own words.

    \item Why is it not practical to keep increasing the number of pipeline stages and thus increasing the ILP?

    \item According to Figure 5, when 8\% of the time is serial, what is the percentage of energy wasted by a 45-processor configuration?

    \item Why can VLIW be a good fit for DSA?

    \item What is your impression regarding Figure 7? Does it change your view of how to program? What are the things that you should be aware of in order to write more efficient software?

    \item Explain what systolic arrays are. How are systolic arrays different from typical SIMD architectures? When were they first created? You should read other sources to get a better understanding of them. Write down the sources you used.

    \item Explain the similarities and differences between Agile software development and Agile hardware development.
\end{enumerate}

Lastly, important concepts from this article will also appear in the final exam.

\end{document}